Investigating soundscapes perception through acoustic scenes simulation

### 2018-09-04 lafaySimulatedScenePerception.tex
fixing typo

We observe a noticeable difference in terms of class choices between the ideal and non-ideal scenes. The distribution of the classes is very similar to the one obtained in a related work on ideal urban soundscapes by~\cite{guastavino2006ideal}, \ie~on one hand, classes involving human presence and nature are prevailing in the ideal scenes, and on the other hand, classes involving mechanical sounds and/or public works are prevailing in the non-ideal scenes. These results confirm a fact previously observed by~\cite{raimbault2005urban,dubois2006cognitive}: the semantic nature of the sound sources play an important role in the assessment of the environment.

>>>>

We observe a noticeable difference in terms of class choices between the ideal and non-ideal scenes. The distribution of the classes is very similar to the one obtained in a related work on ideal urban soundscapes by~\cite{guastavino2006ideal}, \ie~on one hand, classes involving human presence and nature are prevailing in the ideal scenes, and on the other hand, classes involving mechanical sounds and/or public works are prevailing in the non-ideal scenes. These results confirm a fact previously observed by~\cite{raimbault2005urban} and~\cite{dubois2006cognitive}: the semantic nature of the sound sources play an important role in the assessment of the environment.
